---
title: "Survival analysis"
author: "JG 5/24/18"
subtitle: Furunculosis challenge with A.sal. 890054
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This analysis details the survival dynamics of all fish in the infection challenge, along with statistical analysis of the data.

# 1 - Input data

```{r}
# load data
challenge <- read.table("data_IC.csv", header=TRUE, stringsAsFactors = T)

#to only keep true furunculosis deaths (1) and survivors (0)
challenge <- subset(challenge, challenge$Death_Category <= 1) 

# set Baseline (control) as reference level
challenge$Treatment <- factor(challenge$Treatment, levels=c("Infected", "Baseline"))

# only keep cohabitant fish
cohabitants <- subset(challenge, challenge$IP_Injected %in% "No")

# subset carrier fish only
carriers <- subset(challenge, challenge$IP_Injected %in% "Yes")

# view summary
summary(cohabitants)
summary(carriers)
```




************************

# 2 - Survival analysis

## 2.1 - Kaplan-Meier survival curves

Here below are plots of the Kaplan-Meier statistic with 99% confidence intervals. K-M estimates survival probability as a function of cumulative deaths over the amount of individuals at risk for each day post-infection.

```{r}
library(ggplot2)
library(survival)
library(survminer)

# survival fit (cohabs)
cohab <- survfit(Surv(Time_DPI, Death_Category)~Treatment, data=cohabitants, conf.int = 0.99)
summary(cohab)
ggsurvplot(cohab, main="Survival per treatment", pval=TRUE, conf.int=TRUE, risk.table=TRUE)
dev.copy(pdf, "survival_cohabitants.pdf")
dev.off()

# survival fit (carriers)
carr <- survfit(Surv(Time_DPI, Death_Category)~Treatment, data=carriers, conf.int = 0.99)
summary(carr)
ggsurvplot(carr, main="Survival per treatment", pval=TRUE, conf.int=TRUE, risk.table=TRUE)
dev.copy(pdf, "survival_carriers.pdf")
dev.off()

# survival fit (all)
sfit <- survfit(Surv(Time_DPI, Death_Category)~Treatment, data=challenge, conf.int = 0.99)
summary(sfit)
ggsurvplot(sfit, main="Survival per treatment", pval=TRUE, conf.int=TRUE, risk.table=TRUE)
dev.copy(pdf, "survival_all.pdf")
dev.off()

```

